### 2024-12-16 acronyms/acronyms.tex
acronyms
ne529

>>>>

\newacronym{phd}{Ph.D.}{Doctor of Philosophy}
\newacronym{fte}{FTE}{Full Time Equivalent}
\newacronym{ay}{AY}{Academic Year}
\newacronym{hra}{HRA}{Human Reliability Analysis}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{osa}{OSHA}{Occupational Safety and Health Administration}
\newacronym{mtb}{MTBF}{Mean Time Before Failure}
\newacronym{mtf}{MTTF}{Mean Time To Failure}
\newacronym{ecs}{ECCS}{Emergency Core Cooling System}
\newacronym{trp}{THERP}{Technique for Human Error Rate Prediction}
\newacronym{pid}{P\&ID}{Piping \& Instrumentation Diagram}
\newacronym{cdc}{CDC}{Center for Disease Control}
